This is an example of article title

### 2019-08-29 paper.tex
add Measurements demo listing

\begin{equation}
$$\sigma_{G}^{2}=\left(\left.\frac{\partial G}{\partial a}\right|_{a=\overline{a}} \sigma_{a}\right)^{2}+\left(\left.\frac{\partial G}{\partial b}\right|_{b=\overline{b}} \sigma_{b}\right)^{2}+\left(\left.\frac{\partial G}{\partial c}\right|_{c=\overline{c}} \sigma_{c}\right)^{2}+\cdots \\
+2\left(\frac{\partial G}{\partial a}\right)_{a=\overline{a}}\left(\frac{\partial G}{\partial b}\right)_{b=\overline{b}} \sigma_{a b}+2\left(\frac{\partial G}{\partial a}\right)_{a=\overline{a}}\left(\frac{\partial G}{\partial c}\right)_{c=\overline{c}} \sigma_{a c} \\ +2\left(\frac{\partial G}{\partial b}\right)_{b=\overline{b}}\left(\frac{\partial G}{\partial c}\right)_{c=\overline{c}} \sigma_{b c}+\cdots$$

\end{equation}

@@

Unlike a typical non-Julia analytical databases, without any
first class support for Measurements,
Pure-julia analytical database
We can store measurements directly in a JuliaDB table.

@@

@@

>>>>

$$\begin{equation}
  \begin{split}
    \sigma_G^2 &= \left( \left.\frac{\partial G}{\partial a}\right\vert_{a =
        \bar{a}} \sigma_a \right)^2 + \left( \left.\frac{\partial G}{\partial
          b}\right\vert_{b = \bar{b}} \sigma_b \right)^2 + \left(
      \left.\frac{\partial G}{\partial c}\right\vert_{c = \bar{c}} \sigma_c
    \right)^2 + \cdots \\
    &\quad{}+ 2 \left(\frac{\partial G}{\partial a}\right)_{a = \bar{a}}
    \left(\frac{\partial G}{\partial b}\right)_{b = \bar{b}} \sigma_{ab} + 2
    \left(\frac{\partial G}{\partial a}\right)_{a = \bar{a}}
    \left(\frac{\partial G}{\partial c}\right)_{c = \bar{c}}
    \sigma_{ac} \\
    &\quad{}+ 2 \left(\frac{\partial G}{\partial b}\right)_{b = \bar{b}}
    \left(\frac{\partial G}{\partial c}\right)_{c = \bar{c}} \sigma_{bc} +
    \cdots
  \end{split}
\end{equation}
$$

@@

Unlike a typical non-Julia analytical database, without any
first class support for Measurements,
Pure-julia analytical database
We can store measurements directly in a JuliaDB table.

\begin{lstlisting}[language=Julia]
# generate some fake measurements time-series:
using JuliaDB, Measurements, Dates, Random
Random.seed!(1234)

n = 100000
timestamps = sort(DateTime.(now() .- Millisecond.(rand(1:10^6, n))))
x = cumsum(randn(n)) .± rand(n)./10

#=
Table with 100000 rows, 2 columns:
time                     x
────────────────────────────────────────
2019-08-29T01:52:44.148  -1.222±0.086
2019-08-29T01:52:44.178  -0.007±0.02
2019-08-29T01:52:44.201  0.801±0.053
...
=#
\end{lstlisting}

@@

\begin{lstlisting}[language=Julia]
minutely = groupby(mean, observations,
                  :time => t->trunc(t, Minute), select=:x)

#=
Table with 18 rows, 2 columns:
time                 mean
─────────────────────────────────────
2019-08-29T01:52:00  28.1203±0.0015
2019-08-29T01:53:00  59.9434±0.00075
2019-08-29T01:54:00  4.21493±0.00075
...
=#
\end{lstlisting}

@@

\begin{lstlisting}
# assuming session was started with many julia workers

using OnlineStats

d_observations = distribute(observations, 8) # distribute into 8 parts, equally split between available julia processes
d_minutely = groupreduce(Mean(Measurement{Float64}), d_observations,
                         :time => t->trunc(t, Minute), select=:x)

#=
Distributed Table with 18 rows in 1 chunks:
time                 mean
─────────────────────────────────────
2019-08-29T01:52:00  Mean: n=1577 | value=28.1203±0.0015
2019-08-29T01:53:00  Mean: n=5989 | value=59.9434±0.00075
2019-08-29T01:54:00  Mean: n=5883 | value=4.21493±0.00075
...
=#
\end{lstlisting}
